---
title: The Curious Case of Tuftesque Document
#subtitle: Or how I stop worrying about
author: Tahir Enes Gedik
date: '2021-06-08'
slug: try
categories: []
tags: []
---

> I am too lazy to remove this post. So I keep it here to remind me how to make some tweaks.

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
library(tufte)
library(ggstatsplot)
library(ggplot2)
```

```{r}
lorem::ipsum(2)
```

And this is how margin note works.

`r tufte::margin_note("This is a margin **note**.")`

```{r plot, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
df <- carData::Mroz
p <- ggbetweenstats(df,
               x=lfp,
               y=inc) 

# Changing plot background to match the theme
p + theme(plot.background = element_rect(fill = '#fffff8', colour = '#fffff8'),
           panel.background = element_rect(fill="#fffff8"))
```

`r tufte::newthought("And here I am")` with a new thought

  
  <!-- htmltools::includeHTML() below -->
    <html>
      <head>  </head>
      <body>
      <div class="epigraph">
          <blockquote>
            <p>The English language . . . becomes ugly and inaccurate because our thoughts are foolish, but the slovenliness of our language makes it easier for us to have foolish thoughts.</p>
            <footer>George Orwell, “Politics and the English Language”</footer>
          </blockquote>
          <blockquote>
            <p>For a successful technology, reality must take precedence over public relations, for Nature cannot be fooled.</p>
            <footer>Richard P. Feynman, <cite>“What Do You Care What Other People Think?”</cite></footer>
          </blockquote>
          <blockquote>I do not paint things, I paint only the differences between things.<footer>Henri Matisse, <cite>Henri Matisse Dessins: thèmes et variations</cite> (Paris, 1943), 37</footer></blockquote>
        </div>
      </body>
    </html>
  <!-- included above -->


       
